Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-17 surfaces-write-up/surface-write-up.tex
edit references

Our first aim in this section is to prove Theorem ~\ref{thm:proj-generators-relations} bounding the number of generators and relations of $R_D$. Before doing so, we justify the assumption ~\eqref{eqn:bpm-basis-assumption} through a several convincing examples.

@@

In this section, the main aim is to prove Theorem ~\ref{thm:}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.

@@

\begin{proof}
We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
\begin{equation}
\label{eqn:hirz-relations-psi}
	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
\end{equation}

\noindent
for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
^n \bida_j c_j = 0$ and $\bidb_i + \sum_{i=1}^n \bidb_j c_j = 0$.

To find such a $\beta$, we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_4$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i \rfloor$ whenever $i > 4$. \todo{Add $\ell_i$ defenition}

@@

\begin{thm}
\label{thm:hirz-generators-relations}
Let $D = \sum_{i=1}^n \alpha_i D_i$ for curves $D_i$ on $\hirz_k$.  Let $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$.
Then $R_D$ is generated in degree less than 
\[
	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
	\sum_{\substack{i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j
	- \bida_j \bidb_i) \ell_{i, j}
\]

>>>>

Our first aim in this section is to prove Theorem ~\ref{thm:proj-generators-relations} bounding the number of generators and relations of $R_D$. Before doing so, we justify the assumption ~\eqref{eqn:pm-basis-assumption} through a several convincing examples.

@@

In this section, the main aim is to prove Theorem ~\ref{thm:hirz-generators-relations}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.

@@

\begin{proof}
We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ \todo{Aaron: Say where these polynomials live in}
 such that $\psi$ has relations of the form
\begin{equation}
\label{eqn:hirz-relations-psi}
	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
\end{equation}

\noindent
for all $d \in \mathbb{N}$ \todo{Aaron: This confuses me because $d$ is not used above, is $d$ supposed to be $i$?}
 and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
^n \bida_j c_j = 0$ and $\bidb_i + \sum_{i=1}^n \bidb_j c_j = 0$.

To find such a $\beta$, \todo{Aaron: why is there no $i$ subscript? I changed this in the $\bp^m$ case, probably copy past, mutatis mutandis}
 we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_4$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i \rfloor$ whenever $i > 4$. \todo{Add $\ell_i$ defenition}

@@

\begin{thm}
\label{thm:hirz-generators-relations}
Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \hirz_k.$ Let $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$.
Then $R_D$ is generated in degrees at most
\[
	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
	\sum_{\substack{i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j
	- \bida_j \bidb_i) \ell_{i, j}
\]

\noindent
with relations generated in degrees at most 
\[
	\max(2 \sigma, \sigma + \tau)
\]
